Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-07 paper/paper.tex

\begin{figure}[p]
\begin{tabular}{@{}c@{}c@{}}
\hskip -4mm{\epsfig{file=sudoku.eps, height=4cm, width=4.10cm}}
&
{\epsfig{file=lcss.eps, height=4cm, width=4.10cm}}
\\
\hskip -4mm{\epsfig{file=gc_bench.eps, height=4cm, width=4.10cm}}
 &
{\epsfig{file=nperm.eps, height=4cm, width=4.10cm}}
\\
\hskip -4mm{\epsfig{file=fibheap.eps, height=4cm, width=4.10cm}}
&
{\epsfig{file=fibheap.eps, height=4cm, width=4.10cm}}%%Add knightstour.eps
\\
\hskip -4mm{\epsfig{file=nqueens.eps, height=4cm, width=4.10cm}}
&
{\epsfig{file=treejoin.eps, height=4cm, width=4.10cm}}
\end{tabular}
 \caption{Memory  usage  of programs.  The  blue  and the  red  curves
   indicate the number of cons cells  in the active semi-space for LGC
   and  RGC respectively.  The black  curve represents  the number  of
   reachable cells and  the grey curve represents the  number of cells
   that are  actually live (of  which liveness analysis does  a static
   approximation). x-axis is the time measured in number of cons-cells
   allocated. y-axis is the number of cons-cells.}
\label{fig:memory-usage} \figrule
\end{figure}
The  table  in  Figure~\ref{fig:experimental-results} shows  that  LGC
improves the  garbage collection time  and efficiency for most  of the
programs.  Even for  programs where the time taken is  more it is very
competitive.  Memory usage  graphs are shown for  select benchmarks in
Figure~\ref{fig:memory-usage}.  As  the number of  garbage collections
tend  to  be  very large  our  graphs  show  only  a window  which  is
representative of the behavior for  that particular benchmark.  In all
the programs we can see that  the curve corresponding to LGC regularly
dips below the RGC curve.

>>>>

\newcommand{\hgt}{3cm}
\begin{figure*}[t]
\renewcommand{\arraystretch}{.1}
\begin{tabular}{@{}c@{}c@{}}
\hskip -4mm{\epsfig{file=sudoku.eps, height=\hgt}}%, width=4.10cm}}
&
{\epsfig{file=lcss.eps, height=\hgt}}%, width=4.10cm}}
\\
\hskip -4mm{\epsfig{file=gc_bench.eps, height=\hgt}}%
 &
{\epsfig{file=nperm.eps, height=\hgt}}%
\\
\hskip -4mm{\epsfig{file=fibheap.eps, height=\hgt}}%
&
{\epsfig{file=fibheap.eps, height=\hgt}}%%%Add knightstour.eps
\\
\hskip -4mm{\epsfig{file=nqueens.eps, height=\hgt}}%
&
{\epsfig{file=treejoin.eps, height=\hgt}}%
\end{tabular}\vskip -10mm
 \caption{Memory usage  snapshot of  programs.  The  blue and  the red
   curves indicate the  number of cons cells in  the active semi-space
   for  LGC and  RGC  respectively.  The  black  curve represents  the
   number of reachable cells and  the grey curve represents the number
   of cells that are actually live  (of which liveness analysis does a
   static approximation).  x-axis is  the time  measured in  number of
   cons-cells allocated (scaled down by  factor $10^5$). y-axis is the
   number of cons-cells (scaled down by factor $10^3$).}
\label{fig:memory-usage} \figrule
\end{figure*}
The  table  in  Figure~\ref{fig:experimental-results} shows  that  LGC
improves the  garbage collection time  and efficiency for most  of the
programs.  Even for  programs where the time taken is  more it is very
competitive.  Memory usage  graphs are shown for  select benchmarks in
Figure~\ref{fig:memory-usage}.  As  the number of  garbage collections
tend  to  be  very large  our  graphs  show  only  a window  which  is
representative of the behavior for  that particular benchmark.  In all
the programs we can see that  the curve corresponding to LGC regularly
dips below the RGC curve.
